---
title: "AEMs"
author: "Alessio Maggiorelli"
date: "23 08 2022"
output: pdf_document
---

```{r script description}

# This script pre-calculates the AEMs necessary for later scripts

```



```{r TO DO} 


```



```{r questions}


```





# Setup


```{r, setup, include=FALSE}
rm(list = ls())



if(Sys.info()[1] == "Windows"){

  knitr::opts_knit$set(root.dir = "F:/P1/analysis/Rscripts/")
  
} else {

  knitr::opts_knit$set(root.dir = "~/HPC/Project/P1/analysis/Rscripts")
}


```


```{r message=FALSE}

library(stringr)
library(RLRsim)
library(Rcpp)
library(readxl)
library(ordinal)
library(nlme)
library(agridat)
library(emmeans)
library(lme4)
library(plyr)
library(tidyverse)

source("./quick_AEM/main_function.R")

```

# Scenario 1 and 2

## PT AEMs

### load data

```{r}

data <- read_csv(file = "../../data/PT_cleaneddata_expadj_AM.csv")

```

### preliminary data wrangling

```{r}
data <- data %>% 
  # transform into factor
  dplyr::mutate(across(c(G, Block, Reihe, Beet, env_com), as.factor)) 


traits <- c("AUF",
            "AUG",
            "EIN",
            "ENT",
            "ENT.II",
            "ERT_adj",
            "FORM.L",
            "FORM.Q",
            "KNG",
            "RFE",
            "RHI",
            "SCH",
            "SCO",
            "STAE",
            "PPO",
            "SFL",
            "KON",
            "GES",
            "GRA",
            #"WR",
            #"U.pop",
            "U.pop_root",
            "N.pop",
            "UE.pop")


```




### Wrangling

```{r}
# Phenotype data of 2019 WIN
PT_WIN19 <- data %>% 
  filter(year == "2019",
         loc == "WIN") %>% 
  dplyr::arrange(Reihe, Beet)


# Phenotype data of 2020 WIN
PT_WIN20 <- data %>% 
  filter(year == "2020",
         loc == "WIN") %>% 
  dplyr::arrange(Reihe, Beet)


# Phenotype data of 2021 WIN
PT_WIN21 <- data %>% 
  filter(year == "2021",
         loc == "WIN") %>% 
  dplyr::arrange(Reihe, Beet)


# Phenotype data of 2020 GRAN
PT_GRAN20 <- data %>% 
  filter(year == "2020",
         loc == "GRAN") %>% 
  dplyr::arrange(Reihe, Beet)


# Phenotype data of 2021 GRAN
PT_GRAN21 <- data %>% 
  filter(year == "2021",
         loc == "GRAN") %>% 
  dplyr::arrange(Reihe, Beet)


data_list <- list(PT_WIN19,
     PT_WIN20,
     PT_WIN21,
     PT_GRAN20,
     PT_GRAN21)

names(data_list) <- c("PT_WIN19",
     "PT_WIN20",
     "PT_WIN21",
     "PT_GRAN20",
     "PT_GRAN21")


```




### Calculating AEMs

```{r}


AEM_list_sc1 <- list()

for(d in 1:length(data_list)){
  
  
  p_FIX_vector <- vector()
  p_FIX <- "reset"
  
  for(i in 1:length(traits)){
    
    tryCatch({
      
      tryCatch({
      
        # the null model, the model without the random effect we want to test
        m0 <- lmer(get(traits[i]) ~ G + (1|Block) + (1|Reihe), data_list[[d]])
    
        # the alternative model, the model with the random effect we want to test
        mA <- lmer(get(traits[i]) ~ G + (1|Block) + (1|Reihe) + (1|Block:Beet), data_list[[d]])
    
        # the m model, the model with all fixed effects and just the random effect being   tested.
        m  <- lmer(get(traits[i]) ~ G + (1|Block:Beet), data_list[[d]])
        
        
      }, error=function(e){})
        
      tryCatch({
  
      
        p_FIX <- exactRLRT(m0 = m0, 
                    mA = mA,
                    m = m)$p.value
          
  
      }, error=function(e){})
        
      tryCatch({
      
        if(is.character(p_FIX)){
          
          p_FIX <- 1
          
        }
        
      }, error=function(e){})
      
      p_FIX_vector <- c(p_FIX_vector, p_FIX)
      
      p_FIX <- "reset"
      
      rm(m0, mA, m)
      
    }, error = function(e){cat("ERROR :",conditionMessage(e), "\n")})
    
    print(traits[i])
    print(i)
    
  }
  
  model_instruction_df <- data.frame(trait = traits,
                   p_FIX = p_FIX_vector) %>%  
    dplyr::mutate(include_Beet_FIX = case_when(p_FIX > 0.05 ~ FALSE,
                                               TRUE ~ TRUE))
  
  
  
  #### Modelling
  
  fit_list_FG <- list() #fixed Genotype
  
  for (i in 1:length(traits)) {
    
    fit_list_FG[[i]] <- 
      
      tryCatch({
    
        if(model_instruction_df$include_Beet_FIX[i]){
        
          lmer(get(traits[i]) ~ G + (1|Block) + (1|Reihe) + (1|Block:Beet), data_list[[d]])
        
        } else {
        
          lmer(get(traits[i]) ~ G + (1|Block) + (1|Reihe), data_list[[d]])
        
        }
      
    }, error=function(e) {
      
      "No model possible (most likely because of missing PT data)"
      
    })
    
  }
  
  # change the names of the list
  names(fit_list_FG) <- traits
  #length(fit_list_FG)
  
  fit_list_FG <- fit_list_FG[fit_list_FG != "No model possible (most likely because of missing PT data)"]
  
  
  #### AEMS
  
  AEM_FG_list <- list()
  
  for(i in 1:length(fit_list_FG)){
    
    AEM_FG_list[[i]] <- AEM.fun(fit = fit_list_FG[[i]], select.name = "G")$aem
    
  }
  
  names(AEM_FG_list) <- names(fit_list_FG)
  
  
  for (i in names(AEM_FG_list)){
    colnames(AEM_FG_list[[i]]) <- c("G", paste0(i,"_emmean"))
  }
  
  AEM_list_sc1[[d]] <- plyr::join_all(AEM_FG_list, by='G', type='left')
  
}

names(AEM_list_sc1) <- names(data_list)

save(AEM_list_sc1, file = "../results/AEMs/sc1_PT_AEMs_new.Rda")

```





## M AEMs

### load data

```{r}

data <- read_csv(file = "../../data/UAV/NIRS_Data_PMMimp_after_PCoA.csv")

```

### preliminary data wrangling

```{r}
data <- data %>% 
  # transform into factor
  dplyr::mutate(across(c(G, Block, Reife, Reihe, Beet, env_com), as.factor)) 


traits <- data %>% 
  dplyr::select(X530nm_MEAN.D2_imp:X570nm_MEAN.D4_imp) %>% 
  names() %>% as.vector()

```




### Wrangling

```{r}



# Phenotype data of 2020 WIN
H_WIN20 <- data %>% 
  filter(year == "2020",
         loc == "WIN") %>% 
  dplyr::arrange(Reihe, Beet)


# Phenotype data of 2021 WIN
H_WIN21 <- data %>% 
  filter(year == "2021",
         loc == "WIN") %>% 
  dplyr::arrange(Reihe, Beet)


data_list <- list(
     H_WIN20,
     H_WIN21)

names(data_list) <- c("H_WIN20",
     "H_WIN21")


```




### Calculating AEMs

```{r}


AEM_list_sc1 <- list()

for(d in 1:length(data_list)){
  
  # loop through all traits and test for the significance of the Beet effect. Build an   instruction dataframe
  
  p_FIX_vector <- vector()
  p_FIX <- "reset"
  
  for(i in 1:length(traits)){
    
    tryCatch({
      
      tryCatch({
      
        # the null model, the model without the random effect we want to test
        m0 <- lmer(get(traits[i]) ~ G + (1|Block) + (1|Reihe), data_list[[d]])
    
        # the alternative model, the model with the random effect we want to test
        mA <- lmer(get(traits[i]) ~ G + (1|Block) + (1|Reihe) + (1|Block:Beet), data_list[[d]])
    
        # the m model, the model with all fixed effects and just the random effect being   tested.
        m  <- lmer(get(traits[i]) ~ G + (1|Block:Beet), data_list[[d]])
        
        
      }, error=function(e){})
        
      tryCatch({
  
      
        p_FIX <- exactRLRT(m0 = m0, 
                    mA = mA,
                    m = m)$p.value
          
  
      }, error=function(e){})
        
      tryCatch({
      
        if(is.character(p_FIX)){
          
          p_FIX <- 1
          
        }
        
      }, error=function(e){})
      
      p_FIX_vector <- c(p_FIX_vector, p_FIX)
      
      p_FIX <- "reset"
      
      rm(m0, mA, m)
      
    }, error = function(e){cat("ERROR :",conditionMessage(e), "\n")})
    
    print(traits[i])
    print(i)
    
  }
  
  model_instruction_df <- data.frame(trait = traits,
                   p_FIX = p_FIX_vector) %>%  
    dplyr::mutate(include_Beet_FIX = case_when(p_FIX > 0.05 ~ FALSE,
                                               TRUE ~ TRUE))
  
  
  
  #### Modelling
  
  fit_list_FG <- list() #fixed Genotype
  
  for (i in 1:length(traits)) {
    
    fit_list_FG[[i]] <- 
      
      tryCatch({
    
        if(model_instruction_df$include_Beet_FIX[i]){
        
          lmer(get(traits[i]) ~ G + (1|Block) + (1|Reihe) + (1|Block:Beet), data_list[[d]])
        
        } else {
        
          lmer(get(traits[i]) ~ G + (1|Block) + (1|Reihe), data_list[[d]])
        
        }
      
    }, error=function(e) {
      
      "No model possible (most likely because of missing PT data)"
      
    })
    
  }
  
  # change the names of the list
  names(fit_list_FG) <- traits
  #length(fit_list_FG)
  
  fit_list_FG <- fit_list_FG[fit_list_FG != "No model possible (most likely because of missing PT data)"]
  
  
  #### AEMS
  
  AEM_FG_list <- list()
  
  for(i in 1:length(fit_list_FG)){
    
    AEM_FG_list[[i]] <- AEM.fun(fit = fit_list_FG[[i]], select.name = "G")$aem
    
  }
  
  names(AEM_FG_list) <- names(fit_list_FG)
  
  
  for (i in names(AEM_FG_list)){
    colnames(AEM_FG_list[[i]]) <- c("G", paste0(i,"_emmean"))
  }
  
  AEM_list_sc1[[d]] <- plyr::join_all(AEM_FG_list, by='G', type='left')
  
}

names(AEM_list_sc1) <- names(data_list)

save(AEM_list_sc1, file = "../results/AEMs/sc1_H_AEMs_new.Rda")

```



# Scenario 3



## PT AEMs

### load data

```{r}

data <- read_csv(file = "../../data/PT_cleaneddata_expadj_AM.csv")

```

### preliminary data wrangling

```{r}
data <- data %>% 
  # transform into factor
  dplyr::mutate(across(c(G, Block, Reihe, Beet, env_com), as.factor)) 


traits <- c("AUF",
            "AUG",
            "EIN",
            "ENT",
            "ENT.II",
            "ERT_adj",
            "FORM.L",
            "FORM.Q",
            "KNG",
            "RFE",
            "RHI",
            "SCH",
            "SCO",
            "STAE",
            "PPO",
            "SFL",
            "KON",
            "GES",
            "GRA",
            #"WR",
            #"U.pop",
            "U.pop_root",
            "N.pop",
            "UE.pop")


```





### Calculating AEMs

```{r}

  
p_FIX_vector <- vector()
p_FIX <- "reset"

for(i in 1:length(traits)){
  
  tryCatch({
    
    tryCatch({
    
      # the null model, the model without the random effect we want to test
      m0 <- lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe), data)
  
      # the alternative model, the model with the random effect we want to test
      mA <- lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe) + (1|env_com:Block:Beet), data)
  
      # the m model, the model with all fixed effects and just the random effect being  tested.
      m  <- lmer(get(traits[i]) ~ G + (1|env_com:Block:Beet), data)
      
      
    }, error=function(e){})
      
    tryCatch({

    
      p_FIX <- exactRLRT(m0 = m0, 
                  mA = mA,
                  m = m)$p.value
        

    }, error=function(e){})
      
    tryCatch({
    
      if(is.character(p_FIX)){
        
        p_FIX <- 1
        
      }
      
    }, error=function(e){})
    
    p_FIX_vector <- c(p_FIX_vector, p_FIX)
    
    p_FIX <- "reset"
    
    rm(m0, mA, m)
    
  }, error = function(e){cat("ERROR :",conditionMessage(e), "\n")})
  
  print(traits[i])
  print(i)
  
}

model_instruction_df <- data.frame(trait = traits,
                 p_FIX = p_FIX_vector) %>%  
  dplyr::mutate(include_Beet_FIX = case_when(p_FIX > 0.05 ~ FALSE,
                                             TRUE ~ TRUE))



#### Modelling

fit_list_FG <- list() #fixed Genotype

for (i in 1:length(traits)) {
  
  fit_list_FG[[i]] <- 
    
    tryCatch({
  
      if(model_instruction_df$include_Beet_FIX[i]){
      
        lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe) + (1|env_com:Block:Beet), data)
      
      } else {
      
        lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe), data)
      
      }
    
  }, error=function(e) {
    
    "No model possible (most likely because of missing PT data)"
    
  })
  
}

# change the names of the list
names(fit_list_FG) <- traits
#length(fit_list_FG)

fit_list_FG <- fit_list_FG[fit_list_FG != "No model possible (most likely because of issing PT data)"]


#### AEMS

AEM_FG_list <- list()

for(i in 1:length(fit_list_FG)){
  
  AEM_FG_list[[i]] <- AEM.fun(fit = fit_list_FG[[i]], select.name = "G")$aem
  
}

names(AEM_FG_list) <- names(fit_list_FG)


for (i in names(AEM_FG_list)){
  colnames(AEM_FG_list[[i]]) <- c("G", paste0(i,"_emmean"))
}

AEM_list_sc3 <- plyr::join_all(AEM_FG_list, by='G', type='left')
  



save(AEM_list_sc3, file = "../results/AEMs/sc3_PT_AEMs_new.Rda")

```



# Scenario 3 without original env

## PT AEMs

### load data

```{r message=FALSE}

data <- read_csv(file = "../../data/PT_cleaneddata_expadj_AM.csv")

```

### preliminary data wrangling

```{r}
data <- data %>% 
  # transform into factor
  dplyr::mutate(across(c(G, Block, Reihe, Beet, env_com), as.factor)) 


traits <- c("AUF",
            "AUG",
            "EIN",
            "ENT",
            "ENT.II",
            "ERT_adj",
            "FORM.L",
            "FORM.Q",
            "KNG",
            "RFE",
            "RHI",
            "SCH",
            "SCO",
            "STAE",
            "PPO",
            "SFL",
            "KON",
            "GES",
            "GRA",
            #"WR",
            #"U.pop",
            "U.pop_root",
            "N.pop",
            "UE.pop")


```

### Prepare data sets without original environment

```{r}

data_without_WIN20 <- data %>% 
  filter(env_com != "WIN2020")

data_without_WIN21 <- data %>% 
  filter(env_com != "WIN2021")

```




### Calculating AEMs w/o WIN20

```{r}

  
p_FIX_vector <- vector()
p_FIX <- "reset"

for(i in 1:length(traits)){
  
  tryCatch({
    
    tryCatch({
    
      # the null model, the model without the random effect we want to test
      m0 <- lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe), data_without_WIN20)
  
      # the alternative model, the model with the random effect we want to test
      mA <- lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe) + (1|env_com:Block:Beet), data_without_WIN20)
  
      # the m model, the model with all fixed effects and just the random effect being  tested.
      m  <- lmer(get(traits[i]) ~ G + (1|env_com:Block:Beet), data_without_WIN20)
      
      
    }, error=function(e){})
      
    tryCatch({

    
      p_FIX <- exactRLRT(m0 = m0, 
                  mA = mA,
                  m = m)$p.value
        

    }, error=function(e){})
      
    tryCatch({
    
      if(is.character(p_FIX)){
        
        p_FIX <- 1
        
      }
      
    }, error=function(e){})
    
    p_FIX_vector <- c(p_FIX_vector, p_FIX)
    
    p_FIX <- "reset"
    
    rm(m0, mA, m)
    
  }, error = function(e){cat("ERROR :",conditionMessage(e), "\n")})
  
  print(traits[i])
  print(i)
  
}

model_instruction_df <- data.frame(trait = traits,
                 p_FIX = p_FIX_vector) %>%  
  dplyr::mutate(include_Beet_FIX = case_when(p_FIX > 0.05 ~ FALSE,
                                             TRUE ~ TRUE))



#### Modelling

fit_list_FG <- list() #fixed Genotype

for (i in 1:length(traits)) {
  
  fit_list_FG[[i]] <- 
    
    tryCatch({
  
      if(model_instruction_df$include_Beet_FIX[i]){
      
        lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe) + (1|env_com:Block:Beet), data_without_WIN20)
      
      } else {
      
        lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe), data_without_WIN20)
      
      }
    
  }, error=function(e) {
    
    "No model possible (most likely because of missing PT data)"
    
  })
  
}

# change the names of the list
names(fit_list_FG) <- traits
#length(fit_list_FG)

fit_list_FG <- fit_list_FG[fit_list_FG != "No model possible (most likely because of issing PT data)"]


#### AEMS

AEM_FG_list <- list()

for(i in 1:length(fit_list_FG)){
  
  AEM_FG_list[[i]] <- AEM.fun(fit = fit_list_FG[[i]], select.name = "G")$aem
  
}

names(AEM_FG_list) <- names(fit_list_FG)


for (i in names(AEM_FG_list)){
  colnames(AEM_FG_list[[i]]) <- c("G", paste0(i,"_emmean"))
}

AEM_list_sc3_woWIN20 <- plyr::join_all(AEM_FG_list, by='G', type='left')
  



save(AEM_list_sc3_woWIN20, file = "../results/AEMs/sc3_PT_AEMs_woWIN20_new.Rda")

```



### Calculating AEMs w/o WIN21

```{r}

  
p_FIX_vector <- vector()
p_FIX <- "reset"

for(i in 1:length(traits)){
  
  tryCatch({
    
    tryCatch({
    
      # the null model, the model without the random effect we want to test
      m0 <- lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe), data_without_WIN21)
  
      # the alternative model, the model with the random effect we want to test
      mA <- lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe) + (1|env_com:Block:Beet), data_without_WIN21)
  
      # the m model, the model with all fixed effects and just the random effect being  tested.
      m  <- lmer(get(traits[i]) ~ G + (1|env_com:Block:Beet), data_without_WIN21)
      
      
    }, error=function(e){})
      
    tryCatch({

    
      p_FIX <- exactRLRT(m0 = m0, 
                  mA = mA,
                  m = m)$p.value
        

    }, error=function(e){})
      
    tryCatch({
    
      if(is.character(p_FIX)){
        
        p_FIX <- 1
        
      }
      
    }, error=function(e){})
    
    p_FIX_vector <- c(p_FIX_vector, p_FIX)
    
    p_FIX <- "reset"
    
    rm(m0, mA, m)
    
  }, error = function(e){cat("ERROR :",conditionMessage(e), "\n")})
  
  print(traits[i])
  print(i)
  
}

model_instruction_df <- data.frame(trait = traits,
                 p_FIX = p_FIX_vector) %>%  
  dplyr::mutate(include_Beet_FIX = case_when(p_FIX > 0.05 ~ FALSE,
                                             TRUE ~ TRUE))



#### Modelling

fit_list_FG <- list() #fixed Genotype

for (i in 1:length(traits)) {
  
  fit_list_FG[[i]] <- 
    
    tryCatch({
  
      if(model_instruction_df$include_Beet_FIX[i]){
      
        lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe) + (1|env_com:Block:Beet), data_without_WIN21)
      
      } else {
      
        lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe), data_without_WIN21)
      
      }
    
  }, error=function(e) {
    
    "No model possible (most likely because of missing PT data)"
    
  })
  
}

# change the names of the list
names(fit_list_FG) <- traits
#length(fit_list_FG)

fit_list_FG <- fit_list_FG[fit_list_FG != "No model possible (most likely because of missing PT data)"]


#### AEMS

AEM_FG_list <- list()

for(i in 1:length(fit_list_FG)){
  
  AEM_FG_list[[i]] <- AEM.fun(fit = fit_list_FG[[i]], select.name = "G")$aem
  
}

names(AEM_FG_list) <- names(fit_list_FG)


for (i in names(AEM_FG_list)){
  colnames(AEM_FG_list[[i]]) <- c("G", paste0(i,"_emmean"))
}

AEM_list_sc3_woWIN21 <- plyr::join_all(AEM_FG_list, by='G', type='left')
  



save(AEM_list_sc3_woWIN21, file = "../results/AEMs/sc3_PT_AEMs_woWIN21_new.Rda")

```



# Scenario 4



## M AEMs

### load data

```{r}

data <- read_csv(file = "../../data/UAV/NIRS_Data_PMMimp_after_PCoA.csv")

```

### preliminary data wrangling

```{r}
data <- data %>% 
  # transform into factor
  dplyr::mutate(across(c(G, Block, Reihe, Beet, env_com), as.factor)) 


traits <- data %>% 
  dplyr::select(X530nm_MEAN.D2_imp:X570nm_MEAN.D4_imp) %>% 
  names() %>% as.vector()


```





### Calculating AEMs

```{r}

  
p_FIX_vector <- vector()
p_FIX <- "reset"

for(i in 1:length(traits)){
  
  tryCatch({
    
    tryCatch({
    
      # the null model, the model without the random effect we want to test
      m0 <- lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe), data)
  
      # the alternative model, the model with the random effect we want to test
      mA <- lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe) + (1|env_com:Block:Beet), data)
  
      # the m model, the model with all fixed effects and just the random effect being  tested.
      m  <- lmer(get(traits[i]) ~ G + (1|env_com:Block:Beet), data)
      
      
    }, error=function(e){})
      
    tryCatch({

    
      p_FIX <- exactRLRT(m0 = m0, 
                  mA = mA,
                  m = m)$p.value
        

    }, error=function(e){})
      
    tryCatch({
    
      if(is.character(p_FIX)){
        
        p_FIX <- 1
        
      }
      
    }, error=function(e){})
    
    p_FIX_vector <- c(p_FIX_vector, p_FIX)
    
    p_FIX <- "reset"
    
    rm(m0, mA, m)
    
  }, error = function(e){cat("ERROR :",conditionMessage(e), "\n")})
  
  print(traits[i])
  print(i)
  
}

model_instruction_df <- data.frame(trait = traits,
                 p_FIX = p_FIX_vector) %>%  
  dplyr::mutate(include_Beet_FIX = case_when(p_FIX > 0.05 ~ FALSE,
                                             TRUE ~ TRUE))



#### Modelling

fit_list_FG <- list() #fixed Genotype

for (i in 1:length(traits)) {
  
  fit_list_FG[[i]] <- 
    
    tryCatch({
  
      if(model_instruction_df$include_Beet_FIX[i]){
      
        lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe) + (1|env_com:Block:Beet), data)
      
      } else {
      
        lmer(get(traits[i]) ~ G + (1|env_com) + (1|env_com:G) + (1|env_com:Block) + (1|env_com:Reihe), data)
      
      }
    
  }, error=function(e) {
    
    "No model possible (most likely because of missing PT data)"
    
  })
  
}

# change the names of the list
names(fit_list_FG) <- traits
#length(fit_list_FG)


#### AEMS

AEM_FG_list <- list()

for(i in 1:length(fit_list_FG)){
  
  AEM_FG_list[[i]] <- AEM.fun(fit = fit_list_FG[[i]], select.name = "G")$aem
  
}

names(AEM_FG_list) <- names(fit_list_FG)


for (i in names(AEM_FG_list)){
  colnames(AEM_FG_list[[i]]) <- c("G", paste0(i,"_emmean"))
}

AEM_list_sc4 <- plyr::join_all(AEM_FG_list, by='G', type='left')
  



save(AEM_list_sc4, file = "../results/AEMs/sc4_H_AEMs_new.Rda")

```




