---
title: "PS-BLUP"
author: "Alessio Maggiorelli"
output: pdf_document
---


# Setup

```{r, setup, include=FALSE}
rm(list = ls())



if(Sys.info()[1] == "Windows"){

  knitr::opts_knit$set(root.dir = "F:/P1/analysis/Rscripts/")
  
} else {

  knitr::opts_knit$set(root.dir = "~/HPC/Project/P1/analysis/Rscripts")
}


```

```{r packages}

library(data.table)
library(sommer)
library(emmeans)
library(lme4)
library(openxlsx)
library(stringr)
library(tidyverse)
library(AGHmatrix)

```


## Load data

```{r load data}

# phenotype data
PT_data <- read.csv(file = "../../data/PT_cleaneddata_expadj_AM.csv")
# NIRS data
H_data <- read.csv(file = "../../data/UAV/NIRS_Data_PMMimp_after_PCoA.csv")

```

## Define functions

### Data wrangler

```{r UDF data_wrangler}
##########################################
###      Data wrangling function       ###
##########################################

# This function funnels the input data (M and PT data) to the cross-validation function. It mainly searches for matching Genotypes, renames rows and columns and ***calculates the relationship_matrix M (also called H)***.



data_wrangling_for_cv <- function(PT_data, H_data, trait){
  
  # PT_data = PT_AEM_list_sc1[["PT_WIN19"]]
  # H_data = H_AEM_list_sc1[["H_WIN20"]]
  # trait = traits_WIN19
  
  interG <- intersect(PT_data$G, H_data$G)
  
  # then filter PT data for matching Genotypes, arrange in G order and mutate the genotype column as a factor
  PT_data <- PT_data %>% 
  filter(G %in% interG) %>% 
  dplyr::arrange(G) %>% 
  dplyr::mutate(G = as.factor(G))
  
  PT_data$G <- droplevels(PT_data$G)
  
  rownames(PT_data) <- PT_data$G

  H_data <- H_data %>% 
    filter(G %in% interG) %>% 
    dplyr::arrange(G)  
  
  # Convert multispectral data as matrix
  H_matrix <- H_data %>% 
  dplyr::select(-G) %>% 
  as.matrix()
  
  # Rename column names to Genotype names for the multispectral matrix
  rownames(H_matrix) <- PT_data$G
  
  # Calculate relationship matrix
  H <- (H_matrix%*%t(H_matrix))/ncol(H_matrix)
  
  # Rename column and rownames of the relationship matrix to the Genotypes
  colnames(H) <- PT_data$G
  rownames(H) <- PT_data$G
  
  wrangled_data <- list(PT_data = PT_data, 
                        H_matrix = H_matrix, 
                        H = H, 
                        trait_column = PT_data[,trait])
  
  return(wrangled_data)
  
}

```


### MBlup with cross-validation

```{r UDF MBLUP with cross-validation}
##########################################
### X fold cross-validation function   ###
##########################################

# This function computes the M-Blup with cross validation. The number of folds and repititions are adjustable.


cv <- function(phenotype_data, trait, H_data, folds = 5, relationship_matrix, repeats = 25){

  
  # phenotype_data = df$PT_data
  # H_data = df$H_matrix
  # folds = 5
  # relationship_matrix = df$H
  # trait = df$trait_column
  # repeats = 25
  # 
  # create a new correlation object where every correlation result of the folds x repitition cv will be stored
  cor1 <- NULL
  
  
  # For every repeat:
  for(r in 1:repeats){
    
    # r = 1
    
    # Set a new seed (reproducible sets) and split the data into 5 equal folds
    set.seed(r)
    set_in_random_order <- sample(H_data %>% nrow(), replace = FALSE)
    sets <- split(set_in_random_order, cut(seq_along(set_in_random_order), folds, labels = FALSE))

    # For every fold
    for (i in 1:folds) {
      
      # i = 2
      
      # Reset the PT data
      PT_dataset <- phenotype_data
      
      # Set the values for the IDs of the training column to NA (to be predicted)
      train_column <- trait
      train_column[sets[[i]]] <- NA
      
      # append the training column to the data
      PT_dataset <- cbind(PT_dataset, train_column)
      
      # run the M-BLUP; the relationship matrix H is usually calculated beforehand in the function 'data_wrangling_for_cv'
      fit <- mmer(fixed = train_column ~ 1,
                  random = ~vsr(G, Gu = relationship_matrix),
                  rcov = ~vsr(units),
                  data = PT_dataset, verbose = F,
                  date.warning = FALSE)
      
      # Calculate the estimated breeding values
      GEBVs <- fit$Beta$Estimate + fit$U$`u:G`$train_column
      validation_set_index <- match(phenotype_data$G[sets[[i]]], names(GEBVs))
      
      # calculate the correlation between the GEBVs and the predictions of the training column
      cor1 <- c(cor1, cor(trait[sets[[i]]], GEBVs[validation_set_index], use = "pairwise.complete.obs"))
    
    }
    
    print(paste("Repeat", r))
    
  }
  
 return(cor1)
  
}



```


## Wrangle data

```{r data wrangling}

# In this code chunk the data will be molded into data packages for the analysis

# Phenotype data of 2019 WIN
PT_WIN19 <- PT_data %>% 
  filter(year == "2019",
         loc == "WIN") %>% 
  dplyr::arrange(Reihe, Beet)


# Phenotype data of 2020 WIN
PT_WIN20 <- PT_data %>% 
  filter(year == "2020",
         loc == "WIN") %>% 
  dplyr::arrange(Reihe, Beet)


# Phenotype data of 2021 WIN
PT_WIN21 <- PT_data %>% 
  filter(year == "2021",
         loc == "WIN") %>% 
  dplyr::arrange(Reihe, Beet)


# Phenotype data of 2020 GRAN
PT_GRAN20 <- PT_data %>% 
  filter(year == "2020",
         loc == "GRAN") %>% 
  dplyr::arrange(Reihe, Beet)


# Phenotype data of 2021 GRAN
PT_GRAN21 <- PT_data %>% 
  filter(year == "2021",
         loc == "GRAN") %>% 
  dplyr::arrange(Reihe, Beet)


# NIRS data of WIN 2020
H_WIN20 <- H_data %>% 
  filter(env_com == "WIN2020") %>% 
  dplyr::select(Beet,
                Reihe,
                G,
                env_com,
                Reife,
                Block,
                Mutter,
                Vater,
                X530nm_MEAN.D2:X570nm_MEAN.D4_imp)



# NIRS data of WIN 21
H_WIN21 <- H_data %>% 
  filter(env_com == "WIN2021") %>% 
  dplyr::select(Beet,
                Reihe,
                G,
                env_com,
                Reife,
                Block,
                Mutter,
                Vater,
                X530nm_MEAN.D2:X570nm_MEAN.D4_imp)


```

## AEMs

```{r AEMs}

load("../results/AEMs/sc1_PT_AEMs_new.Rda")
PT_AEM_list_sc1 <- AEM_list_sc1
load("../results/AEMs/sc1_H_AEMs_new.Rda")
H_AEM_list_sc1 <- AEM_list_sc1
load("../results/AEMs/sc3_PT_AEMs_new.Rda")
load("../results/AEMs/sc3_PT_AEMs_woWIN20_new.Rda")
load("../results/AEMs/sc3_PT_AEMs_woWIN21_new.Rda")


```


## Traits analysed


```{r}

# For every PT dataset, depending on the year and location not every trait can be analysed (due to missing trait data)

# In this code chunk we will find analysable trait data for each PT dataset

#-----------------

# These are the sets of all possible traits

traits <- c(
  "AUF_emmean",
  "AUG_emmean",
  "EIN_emmean",
  "ENT_emmean",
  "ENT.II_emmean",
  "ERT_adj_emmean",
  "FORM.L_emmean",
  "FORM.Q_emmean",
  "KNG_emmean",
  "RFE_emmean",
  "RHI_emmean",
  "SCH_emmean",
  "SCO_emmean",
  "STAE_emmean",
  "PPO_emmean",
  "SFL_emmean",
  "KON_emmean",
  "GES_emmean",
  "GRA_emmean",
  #"ZW_emmean",
  #"WR_emmean",
  #"U.pop_emmean",
  "U.pop_root_emmean",
  "N.pop_emmean",
  "UE.pop_emmean")

# these are the analysable traits for each environment

traits_WIN19 <- PT_AEM_list_sc1[["PT_WIN19"]] %>%
  dplyr::select(-G) %>% 
  names()

traits_WIN20 <- PT_AEM_list_sc1[["PT_WIN20"]] %>%
  dplyr::select(-G) %>% 
  names()

traits_WIN21 <- PT_AEM_list_sc1[["PT_WIN21"]] %>%
  dplyr::select(-G) %>% 
  names()


traits_GRAN20 <- PT_AEM_list_sc1[["PT_GRAN20"]] %>%
  dplyr::select(-G) %>% 
  names()

traits_GRAN21 <- PT_AEM_list_sc1[["PT_GRAN21"]] %>%
  dplyr::select(-G) %>% 
  names()



#--------------

traits_PTAEM <- AEM_list_sc3 %>%
  dplyr::select(-G) %>% 
  names()



```



# Scenario 1 and 2

## Calculations H2020

### PTWIN19 x HWIN20

```{r}

# predict WIN19 PT with WIN20 NIRS

results_PTWIN19_HWIN20_per_trait <- list()
  
for (t in traits_WIN19) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN19"]],
                              H_data = H_AEM_list_sc1[["H_WIN20"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTWIN19_HWIN20_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTWIN19_HWIN20_per_trait, 
     file = "../results/H-BLUP/PTWIN19_x_HWIN20_new.Rda")


```


### PTWIN20 x HWIN20

```{r}


results_PTWIN20_HWIN20_per_trait <- list()
  
for (t in traits_WIN20) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN20"]],
                              H_data = H_AEM_list_sc1[["H_WIN20"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTWIN20_HWIN20_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTWIN20_HWIN20_per_trait, 
     file = "../results/H-BLUP/PTWIN20_x_HWIN20_new.Rda")


```


### PTWIN21 x HWIN20

```{r}

results_PTWIN21_HWIN20_per_trait <- list()
  
for (t in traits_WIN21) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN21"]],
                              H_data = H_AEM_list_sc1[["H_WIN20"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTWIN21_HWIN20_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTWIN21_HWIN20_per_trait, 
     file = "../results/H-BLUP/PTWIN21_x_HWIN20_new.Rda")


```


### PTGRAN20 x HWIN20

```{r}


results_PTGRAN20_HWIN20_per_trait <- list()
  
for (t in traits_GRAN20) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_GRAN20"]],
                              H_data = H_AEM_list_sc1[["H_WIN20"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTGRAN20_HWIN20_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTGRAN20_HWIN20_per_trait, 
     file = "../results/H-BLUP/PTGRAN20_x_HWIN20_new.Rda")



```


### PTGRAN21 x HWIN20

```{r}

# predict GRAN21 PT with WIN20 NIRS

results_PTGRAN21_HWIN20_per_trait <- list()
  
for (t in traits_GRAN21) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_GRAN21"]],
                              H_data = H_AEM_list_sc1[["H_WIN20"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTGRAN21_HWIN20_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTGRAN21_HWIN20_per_trait, 
     file = "../results/H-BLUP/PTGRAN21_x_HWIN20_new.Rda")



```


## Calculations H2021

### PTWIN19 x HWIN21

```{r}

results_PTWIN19_HWIN21_per_trait <- list()
  
for (t in traits_WIN19) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN19"]],
                              H_data = H_AEM_list_sc1[["H_WIN21"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTWIN19_HWIN21_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}

save(results_PTWIN19_HWIN21_per_trait, 
     file = "../results/H-BLUP/PTWIN19_x_HWIN21_new.Rda")


```


### PTWIN20 x HWIN21

```{r}

results_PTWIN20_HWIN21_per_trait <- list()
  
for (t in traits_WIN20) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN20"]],
                              H_data = H_AEM_list_sc1[["H_WIN21"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTWIN20_HWIN21_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}

save(results_PTWIN20_HWIN21_per_trait, 
     file = "../results/H-BLUP/PTWIN20_x_HWIN21_new.Rda")


```


### PTWIN21 x HWIN21

```{r}

results_PTWIN21_HWIN21_per_trait <- list()
  
for (t in traits_WIN21) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN21"]],
                              H_data = H_AEM_list_sc1[["H_WIN21"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTWIN21_HWIN21_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}

save(results_PTWIN21_HWIN21_per_trait, 
     file = "../results/H-BLUP/PTWIN21_x_HWIN21_new.Rda")


```



### PTGRAN20 x HWIN21

```{r}

results_PTGRAN20_HWIN21_per_trait <- list()
  
for (t in traits_GRAN20) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_GRAN20"]],
                              H_data = H_AEM_list_sc1[["H_WIN21"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTGRAN20_HWIN21_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}

save(results_PTGRAN20_HWIN21_per_trait, 
     file = "../results/H-BLUP/PTGRAN20_x_HWIN21_new.Rda")


```


### PTGRAN21 x HWIN21

```{r}

results_PTGRAN21_HWIN21_per_trait <- list()
  
for (t in traits_GRAN21) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_GRAN21"]],
                              H_data = H_AEM_list_sc1[["H_WIN21"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTGRAN21_HWIN21_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}

save(results_PTGRAN21_HWIN21_per_trait, 
     file = "../results/H-BLUP/PTGRAN21_x_HWIN21_new.Rda")


```



# Scenario 3

## Calculate H2020

```{r}

# predict AEMs of PT data with WIN20 H data

results_PTAEM_HWIN20_per_trait <- list()
  
for (t in traits_PTAEM) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = AEM_list_sc3,
                              H_data = H_AEM_list_sc1[["H_WIN20"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTAEM_HWIN20_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTAEM_HWIN20_per_trait, 
     file = "../results/H-BLUP/PTAEM_x_HWIN20_new.Rda")




```




## Calculate H2021

```{r}

# predict AEMs of PT data with WIN21 H data

results_PTAEM_HWIN21_per_trait <- list()
  
for (t in traits_PTAEM) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = AEM_list_sc3,
                              H_data = H_AEM_list_sc1[["H_WIN21"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTAEM_HWIN21_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTAEM_HWIN21_per_trait, 
     file = "../results/H-BLUP/PTAEM_x_HWIN21_new.Rda")



```


# Scenario 3 without original env

## Calculate H2020 and predict AEMs without PT2020

```{r}

# predict AEMs of PT data (AEMs were calculated witout WIN2020) with WIN20 multispectral data

results_PTAEMwoWIN20_HWIN20_per_trait <- list()
  
for (t in traits_PTAEM) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for M-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = AEM_list_sc3_woWIN20,
                              H_data = H_AEM_list_sc1[["H_WIN20"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv M-BLUP for every trait of the PT_data environment
  results_PTAEMwoWIN20_HWIN20_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTAEMwoWIN20_HWIN20_per_trait, 
     file = "../results/H-BLUP/PTAEMwoWIN20_x_HWIN20_new.Rda")




```


## Calculate H2021 and predict AEMs without PT2021

```{r}

# predict AEMs of PT data (AEMs were calculated witout WIN2020) with WIN20 multispectral data

results_PTAEMwoWIN21_HWIN21_per_trait <- list()
  
for (t in traits_PTAEM) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for M-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = AEM_list_sc3_woWIN21,
                              H_data = H_AEM_list_sc1[["H_WIN21"]],
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv M-BLUP for every trait of the PT_data environment
  results_PTAEMwoWIN21_HWIN21_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTAEMwoWIN21_HWIN21_per_trait, 
     file = "../results/H-BLUP/PTAEMwoWIN21_x_HWIN21_new.Rda")




```



# Scenario 4.1 AEMs

## Load AEMs

```{r}

load("../results/AEMs/sc4_H_AEMs_new.Rda")


```


## Traits analysed


```{r}

# For every PT dataset, depending on the year and location not every trait can be analysed (due to missing trait data)

# In this code chunk we will find analysable trait data for each PT dataset

#-----------------

# These are the sets of all possible traits

traits <- c(
  "AUF_emmean",
  "AUG_emmean",
  "EIN_emmean",
  "ENT_emmean",
  "ENT.II_emmean",
  "ERT_adj_emmean",
  "FORM.L_emmean",
  "FORM.Q_emmean",
  "KNG_emmean",
  "RFE_emmean",
  "RHI_emmean",
  "SCH_emmean",
  "SCO_emmean",
  "STAE_emmean",
  "PPO_emmean",
  "SFL_emmean",
  "KON_emmean",
  "GES_emmean",
  "GRA_emmean",
  #"ZW_emmean",
  #"WR_emmean",
  #"U.pop_emmean",
  "U.pop_root_emmean",
  "N.pop_emmean",
  "UE.pop_emmean")

# these are the analysable traits for PT AEM data

traits_PTAEM <- AEM_list_sc3 %>%
  dplyr::select(-G) %>% 
  names()



# these are the analysable traits for each environment

traits_WIN19 <- PT_AEM_list_sc1[["PT_WIN19"]] %>%
  dplyr::select(-G) %>% 
  names()

traits_WIN20 <- PT_AEM_list_sc1[["PT_WIN20"]] %>%
  dplyr::select(-G) %>% 
  names()

traits_WIN21 <- PT_AEM_list_sc1[["PT_WIN21"]] %>%
  dplyr::select(-G) %>% 
  names()


traits_GRAN20 <- PT_AEM_list_sc1[["PT_GRAN20"]] %>%
  dplyr::select(-G) %>% 
  names()

traits_GRAN21 <- PT_AEM_list_sc1[["PT_GRAN21"]] %>%
  dplyr::select(-G) %>% 
  names()



```



## Single ENVs

### PTWIN19 x HAEM

```{r}

# predict PTWIN19 with H AEMs data

results_PTWIN19_HAEM_per_trait <- list()
  
for (t in traits_WIN19) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN19"]],
                              H_data = AEM_list_sc4,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTWIN19_HAEM_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTWIN19_HAEM_per_trait, 
     file = "../results/H-BLUP/PTWIN19_x_HAEM_new.Rda")




```



### PTWIN20 x HAEM

```{r}

results_PTWIN20_HAEM_per_trait <- list()
  
for (t in traits_WIN20) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN20"]],
                              H_data = AEM_list_sc4,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTWIN20_HAEM_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTWIN20_HAEM_per_trait, 
     file = "../results/H-BLUP/PTWIN20_x_HAEM_new.Rda")




```



### PTWIN21 x HAEM

```{r}

results_PTWIN21_HAEM_per_trait <- list()
  
for (t in traits_WIN21) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN21"]],
                              H_data = AEM_list_sc4,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTWIN21_HAEM_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTWIN21_HAEM_per_trait, 
     file = "../results/H-BLUP/PTWIN21_x_HAEM_new.Rda")




```


### PTGRAN20 x HAEM

```{r}

results_PTGRAN20_HAEM_per_trait <- list()
  
for (t in traits_GRAN20) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_GRAN20"]],
                              H_data = AEM_list_sc4,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTGRAN20_HAEM_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTGRAN20_HAEM_per_trait, 
     file = "../results/H-BLUP/PTGRAN20_x_HAEM_new.Rda")




```


### PTGRAN21 x HAEM

```{r}

results_PTGRAN21_HAEM_per_trait <- list()
  
for (t in traits_GRAN21) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_GRAN21"]],
                              H_data = AEM_list_sc4,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTGRAN21_HAEM_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTGRAN21_HAEM_per_trait, 
     file = "../results/H-BLUP/PTGRAN21_x_HAEM_new.Rda")




```

## AEM ENV

### PTAEM x HAEM

```{r}

results_PTAEM_HAEM_per_trait <- list()
  
for (t in traits_PTAEM) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = AEM_list_sc3,
                              H_data = AEM_list_sc4,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTAEM_HAEM_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTAEM_HAEM_per_trait, 
     file = "../results/H-BLUP/PTAEM_x_HAEM_new.Rda")




```


# Scenario 4.2 c-join

## Wrangling

```{r}
# in this scenario the multispectral data of both environments will be combined by using each env x channel combination as a new predictor (column joining). That means we have to search for matching Genotypes that occur in both years
names(AEM_list_sc1$H_WIN20) <- paste0(names(AEM_list_sc1$H_WIN20), "_WIN20")
names(AEM_list_sc1$H_WIN21) <- paste0(names(AEM_list_sc1$H_WIN21), "_WIN21")
  
AEM_list_sc4.2 <- AEM_list_sc1$H_WIN20 %>% 
  cbind(AEM_list_sc1$H_WIN21) %>% 
  dplyr::select("G" = G_WIN20,
                everything(),
                -G_WIN21)



```


## Single ENVs

### PTWIN19 x cjH

```{r}

# predict PTWIN19 with column joined H data of both envs

results_PTWIN19_cjH_per_trait <- list()
  
for (t in traits_WIN19) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN19"]],
                              H_data = AEM_list_sc4.2,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment but with the newly build column-joined relationship matrix 
  results_PTWIN19_cjH_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTWIN19_cjH_per_trait, 
     file = "../results/H-BLUP/PTWIN19_x_cjH_new.Rda")


```


### PTWIN20 x cjH

```{r}


results_PTWIN20_cjH_per_trait <- list()
  
for (t in traits_WIN20) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN20"]],
                              H_data = AEM_list_sc4.2,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment but with the newly build column-joined relationship matrix 
  results_PTWIN20_cjH_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTWIN20_cjH_per_trait, 
     file = "../results/H-BLUP/PTWIN20_x_cjH_new.Rda")


```



### PTWIN21 x cjH

```{r}


results_PTWIN21_cjH_per_trait <- list()
  
for (t in traits_WIN21) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_WIN21"]],
                              H_data = AEM_list_sc4.2,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment but with the newly build column-joined relationship matrix 
  results_PTWIN21_cjH_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTWIN21_cjH_per_trait, 
     file = "../results/H-BLUP/PTWIN21_x_cjH_new.Rda")


```



### PTGRAN20 x cjH

```{r}


results_PTGRAN20_cjH_per_trait <- list()
  
for (t in traits_GRAN20) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_GRAN20"]],
                              H_data = AEM_list_sc4.2,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment but with the newly build column-joined relationship matrix 
  results_PTGRAN20_cjH_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTGRAN20_cjH_per_trait, 
     file = "../results/H-BLUP/PTGRAN20_x_cjH_new.Rda")


```



### PTGRAN21 x cjH

```{r}


results_PTGRAN21_cjH_per_trait <- list()
  
for (t in traits_GRAN21) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = PT_AEM_list_sc1[["PT_GRAN21"]],
                              H_data = AEM_list_sc4.2,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment but with the newly build column-joined relationship matrix 
  results_PTGRAN21_cjH_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTGRAN21_cjH_per_trait, 
     file = "../results/H-BLUP/PTGRAN21_x_cjH_new.Rda")


```


## AEM ENV

### PTAEM x cjH

```{r}

results_PTAEM_cjH_per_trait <- list()
  
for (t in traits_PTAEM) {
  
  print(paste("calculating", t, "..."))
  
  # Prepare the data for H-BLUP cv for all traits available for the PT environment one at a time
  df <- data_wrangling_for_cv(PT_data = AEM_list_sc3,
                              H_data = AEM_list_sc4.2,
                              trait = t) #t
  
  # Do the 5 fold 25 repititions cv H-BLUP for every trait of the PT_data environment
  results_PTAEM_cjH_per_trait[[t]] <- cv(phenotype_data = df$PT_data,
                                                H_data = df$H_matrix,
                                                folds = 5,
                                                relationship_matrix = df$H,
                                                trait = df$trait_column,
                                                repeats = 25)
  
  
  
  
}


save(results_PTAEM_cjH_per_trait, 
     file = "../results/H-BLUP/PTAEM_x_cjH_new.Rda")




```




